|

### 2019-07-04 inst/manuscript/manuscript.Rmd
Add full introduction

>>>>

Extracellular vesicles (EVs) are key factors in the progression of many diseases 
ranging from cancer [@xu2018] to neurodegenerative diseases [@quek2017] and 
bacterial infections [@pathirana2016]. EVs are defined as “particles naturally 
released from the cell that are delimited by a lipid bilayer and cannot 
replicate” [@thery2018]. Packaging of cargo into EVs is a method for the 
coordinated release of biological molecules via a non-classic method of 
secretion.  This facilitates intercellular communication both within an 
organism [@maas2017] and between organisms [@schorey2015].

Recently, EVs have 
been proposed to function in the pathogenesis of fungal disease, particularly 
in yeast infections including those from the genera _Cryptococcus_ 
[@bielska2018; @oliveira2010b; @rodrigues2008], _Paracoccidioides_ 
[@dasilva2015a; @vallejo2011], and _Candida_ 
[@joffe2016; @vargas2015; @wolf2015]. The cargo of fungal EVs comprises 
proteins [@bleackley2019], nucleic acids [@dasilva2015], lipids 
[@oliveira2009; @rodrigues2007; @vargas2015; @wolf2015] and carbohydrates 
[@dasilva2015a; @rodrigues2007]. Fungal EVs activate innate immune cells in 
vitro [@dasilva2016; @oliveira2010b; @vargas2015; @wolf2015] and are responsible 
for the hypervirulence of a _Cryptococcus gattii_ strain that caused disease in 
immunocompetent individuals [@bielska2018]. Given the potential roles for EVs in 
host-pathogen interactions, there is significant motivation to better understand 
the biology of fungal EVs.

_C. albicans_ EVs are typical of fungal EVs. They contain proteins, lipids, 
nucleic acids and carbohydrates 
[@dasilva2015; @gil-bona2015b; @vargas2015; @wolf2015; @zarnowski2018]. 
Activation of murine macrophages and dendritic cells by EVs from _C. albicans_ 
indicates a potential role for EVs in modulating the innate immune response to 
the fungus [@vargas2015; @wolf2015]. Formation of biofilms is a critical 
component of _C. albicans_ pathogenesis [@nobile2015] and the biofilm matrix 
provides a protective layer for the fungus against antifungal drugs [@taff2012]. 
The cargo of EVs produced by _C. albicans_ biofilms includes key proteins and 
carbohydrates for biofilm biogenesis, making EVs crucial contributors to the 
establishment of biofilms [@zarnowski2018]. Furthermore, “add-back” of EVs from 
wildtype biofilms restored the loss of azole resistance in biofilms formed by 
strains with deletions in genes encoding important enzymes for matrix 
generation [@zarnowski2018]. That is, EVs also function in antifungal drug 
resistance.

The tools and techniques for the study of fungal EVs have been adapted from 
those established for mammalian systems, where EVs are most intensively 
studied. Many of the cutting-edge experimental techniques for isolation, 
tracking, and analysis of mammalian EVs are dependent on protein markers 
[@lotvall2014]. They include identifying fractions containing EVs after density 
gradient centrifugation [@greening2015] or size exclusion chromatography 
[@gamez-valero2016], purification of EVs via immunoaffinity capture [@oksvold2015], 
and imaging of EV release and uptake [@suetsugu2013]. Unfortunately, proteomic 
analyses of fungal EVs have revealed that the markers that have been so useful 
for the isolation and study of mammalian EVs are not present in fungal EVs 
[@bleackley2019]. Thus, there are differences in the protein cargo and possibly 
the biogenesis of EVs from fungi and mammalian cells, and _de novo_ 
identification of fungal EV markers is essential. Inconsistencies between 
published data sets on the protein content of fungal EVs [@bleackley2019] means 
that a robust proteomic analysis of EVs from a particular species is required 
to provide an adequate data set for EV marker identification. In this study, we 
have addressed this problem by performing in-depth proteomic analyses on 
multiple _C. albicans_ strains to define a set of broadly applicable 
_C. albicans_ EV markers.

We employed label-free quantitative proteomics to generate EV and whole cell 
lysate (WCL) proteomes for a selection of different _C. albicans_ strains and 
morphologies; DAY286 yeast, DAY286 biofilm, ATCC90028 yeast, and ATCC10231 
yeast. By comparing the EV versus WCL data across all four strains we 
identified 39 putative EV markers which are enriched in _C. albicans_ EVs 
regardless of source, cell strain, or morphology. These candidate protein 
markers include GTPases, enzymes crucial for cell wall synthesis, and 
plasma membrane proteins resembling mammalian tetraspanins or claudins. 
The “minimal information for studies of EVs” (MISEV) 2018 position statement 
indicates that, in addition to demonstrating the enrichment of EV marker 
proteins in EV preparations, a deficiency of non-EV proteins should also be 
shown [@thery2018]. With this in mind, we identified 40 proteins that were 
depleted in _C. albicans_ EVs compared to the WCL from the four strains. 
Validation of these putative EV markers in vitro will allow future _C. albicans_ 
EV research to align better with the recommendations set out in MISEV2018. 
Furthermore, robust _C. albicans_ EV markers will allow adaptation of mammalian 
EV analysis techniques for use in the study of EVs in _C. albicans_ pathogenesis 
and will provide potential new targets for the development of novel antifungals.
